### 2018-08-01 paper/system-model.tex
minor system model

% -*- tex-main-file: "contents.tex" compile-command: "pdflatex -halt-on-error p2p-private-cloud.tex > /dev/null" ispell-dictionary: "american" -*-

@@

In the following, we first describe \changeFT{how file sharing typically occurs when users rely on a cloud storage provider. We use this simple use case}
%a simple model of data sharing via cloud storage
to
highlight some of the desirable privacy properties of a file sharing service, before mapping them into our \changeFT{fully decentralized (a.k.a P2P)}
context. 
We finally consider the additional privacy properties required to protect users from  network traffic analysis, which we propose to address through onion
routing, and detail our adversary model. \commentFT{I wasn't sure how to position onion routing: to me it is more a solution than a problem specification, and since we are describing what we want here (spec./problem space) I wasn't sure how much to highlight onion routing (solution space).} \commentFT{Terminology: Do we use both `fully decentralized' and `P2P', or do we favor one over the other?}

@@

The use of the cloud provider, as a third party,
provides two main privacy properties, which we \changeFT{should preserve} when
moving to a \ac{P2P}~\cite{DevilInMetadata} setting:
\begin{itemize}
\item Except for the cloud provider, Alice and Bob are the only \changeFT{users} who learn 
about Alice sharing a file with Bob. \sonja{narrow down to users?} \commentFT{Changed to users: we could also use entities/participants}
\item
  The composition and behavior of Alice and Bob's \squad remain hidden to each other, and to other users. I.e. Alice does not learn which devices Bob owns or uses, let alone how Bob uses them, and reciprocally. 
%%   Alice and Bob learn nothing about each others' devices, \ie 
%% they cannot map any device as belonging to each other or draw
%% inferences from their behavior.
The cloud provider, however, \changeFT{knows this information}. \sonja{expand to other users?} \commentFT{Done}
\end{itemize}

@@

Friendly surveillance can be mitigated by ensuring security properties 
typically associated with onion routing \cite{CLOnionRouting}: 
% We combine the requirements from
% the \ac{P2P} setting with those from onion routing for anonymity.
% Camenisch and Lysianskaya \cite{CLOnionRouting} define security properties 
% for onion routing:
correctness, integrity, security (wrap resistance,
indistinguishability). These properties cover the concerns about
revealing to others that Alice shares a file with Bob in the first
place. In \name, we additionally derive the property of
device-unlinkability from the \ac{P2P} requirements, meaning that
using \name does not reveal the \squad a device belongs to nor the
owner and can thus not infer anything about a user's behavior such as
being online.

\paragraph*{Adversary model} To assess our approach, we use the adversary model assumed by by Tor \cite{} and
Sphinx \cite{}: the adversary has complete control over some part of
the network as well as some of the nodes. We not consider a passive
global network adversary, against which it is notoriously difficult to
achieve security~\cite{SystemsForAnonymousCommunication}.

>>>>

% -*- tex-main-file: "contents.tex" compile-command: "pdflatex -halt-on-error p2p-private-cloud.tex > /dev/null" ispell-dictionary: "american" -*-
%!TEX root = p2p-private-cloud.tex

@@

In the following, we first describe \changeFT{how file sharing typically occurs when users rely on a cloud storage provider. We use this simple use case}
%a simple model of data sharing via cloud storage
to
highlight some of the desirable privacy properties of a file sharing service, before mapping them into our \changeFT{fully decentralized (a.k.a. P2P)}
context. 
We finally consider the additional privacy properties required to protect users from  network traffic analysis, which we propose to address through onion
routing, and detail our adversary model. \commentFT{I wasn't sure how to position onion routing: to me it is more a solution than a problem specification, and since we are describing what we want here (spec./problem space) I wasn't sure how much to highlight onion routing (solution space).} \commentFT{Terminology: Do we use both `fully decentralized' and `P2P', or do we favor one over the other?}

@@

The use of the cloud provider, as a third party,
provides two main privacy properties, which we \changeFT{should preserve} when
moving to a \ac{P2P}~\cite{DevilInMetadata} setting:
\begin{itemize}
\item Except for the cloud provider, Alice and Bob are the only \changeFT{users} who learn 
about Alice sharing a file with Bob; \sonja{narrow down to users?} \commentFT{Changed to users: we could also use entities/participants}
\item
  The composition and behavior of Alice and Bob's \squad remain hidden to each other, and to other users. I.e. Alice does not learn which devices Bob owns or uses, let alone how Bob uses them, and reciprocally. 
%%   Alice and Bob learn nothing about each others' devices, \ie 
%% they cannot map any device as belonging to each other or draw
%% inferences from their behavior.
The cloud provider, however, \changeFT{knows this information}. \sonja{expand to other users?} \commentFT{Done}
\end{itemize}

@@

Friendly surveillance can be mitigated by ensuring security properties 
typically associated with onion routing \cite{CLOnionRouting}: 
% We combine the requirements from
% the \ac{P2P} setting with those from onion routing for anonymity.
% Camenisch and Lysianskaya \cite{CLOnionRouting} define security properties 
% for onion routing:
correctness, integrity, security (wrap resistance,
indistinguishability). These properties cover the concerns about
revealing to others that Alice shares a file with Bob in the first
place. In \name, we additionally derive the property of
device-unlinkability from the \ac{P2P} requirements, meaning that
using \name does not reveal the \squad a device belongs to nor its
owner. \changeAL{Thus, no information on the user's behavior (e.g. being online) can be infered through \name.} 
%and can thus not infer anything about a user's behavior such as being online.

\paragraph*{Adversary model} To assess our approach, we use the adversary model assumed by Tor~\cite{Tor} and
Sphinx~\cite{Sphinx}: the adversary has complete control over some part of
the network as well as some of the nodes. We do not consider a passive
global network adversary, against which it is notoriously difficult to
achieve security~\cite{SystemsForAnonymousCommunication}.
